Conductive and convective heat transfer in inductive heating of subsea buried pipelines

### 2021-10-14 manuscript.tex
:pencil: Minor edits to critical Ra in introduction

Experimental results on heat transfer through saturated glass beads show that high permeable soil increases the convective heat transfer~\cite{fand1986natural}. \citeN{hardee1976boundary} and~\citeN{merkin1979free} developed analytical solutions for heat transfer from a cylinder embedded in a porous media considering natural convective flow. However, none of these authors identified a conduction region.~\citeNP{nield1968onset}  separated conduction and convection regions using a non-dimensional Rayleigh-Darcy number for a constant temperature source in a rectangular domain.~\citeNP{nield1968onset} established a critical Rayleigh-Darcy number of 12 separating conduction from convection-dominated flows for a rectangular domain with a constant heat source. As the boundary conditions in inductive heating of pipeline are different, the applicability of the critical Rayleigh-Darcy number of 12 to this submarine condition is unknown. The Rayleigh number quantifies the proportion of conduction or convection flow. Although the heat transfer is related to the type of flow in the porous media, the relationship is not linear. Hence, the Rayleigh number only determines the mode of flow, conduction or convection, and does not help determine the amount of heat transfer.

>>>>

Experimental results on heat transfer through saturated glass beads show that high permeable soil increases the convective heat transfer~\cite{fand1986natural}. \citeN{hardee1976boundary} and~\citeN{merkin1979free} developed analytical solutions for heat transfer from a cylinder embedded in a porous media considering natural convective flow. However, none of these authors identified a conduction region.~\citeN{nield1968onset}  separated conduction and convection regions using a non-dimensional Rayleigh-Darcy number.~\citeN{nield1968onset} established a critical Rayleigh-Darcy number of 12 separating conduction from convection-dominated flows for a rectangular domain with a constant heat source. The applicability of this critical Rayleigh-Darcy number of 12 to this submarine condition is unknown due to differences in boundary conditions and asymmetric nature of the problem.

The Rayleigh number only quantifies the proportion of conduction or convection flow, and not the amount of heat transfer through these different modes. Although the heat transfer is related to the type of flow in the porous media, the relationship is not linear. Hence, we need to develop new relationships between the amount of conductive and convective flow and the corresponding heat loss in each mode. By computing the amount of heat lost in convection and conduction, we will identify the favorable and unfavorable conditions for inductive heat transfer in heating submarine pipelines.
